\chapter{\chapterlongname \thechapter}


\section{Defining terms}

\begin{enumerate}

	\item Read the following excerpt from the course syllabus.
	
	\begin{reading}
%		\begin{quote}
			In this course, we will explore fundamental physical phenomena, like freezing things or moving objects. Instead of ``covering'' topics and ``presenting facts,'' we will make sense of these phenomena together using tools that physicists use: \textbf{\em models}.
			
			Using what we know today about how people (including scientists!) learn, we have structured this course around collaborative discussion/lab sections. In these sections, you will participate in various types of activities, experiments, and discussions in smaller and bigger groups. Between lab meetings, you will do, reflect, and prepare by doing homework assignments that we will elaborate together in the lab sections. The lecture is designed to allow all of us to get together as a community to reflect on what you experienced in the lab sections.
%		\end{quote}
	\end{reading}
	
	\item In the space below, \textbf{individually}, write out what you think it means to ``Do Science'' in this course.
	
	\vspace{2in}

Once you have all written something down, discuss your response in your \textbf{small group}. After your group reaches a consensus, write your response on your group's whiteboard.
\end{enumerate}

\WCD
	
\section{Setting some goals}

\begin{enumerate}
	\item In the space below, \textbf{individually}, write out 
	\begin{enumerate}
		\item at least one goal you want to achieve regarding ``doing science.''
		\item at least one goal for the whole class to achieve regarding ``doing science.''
	\end{enumerate}
	Remember to address to ``doing science'' in the way the class has defined it.
	
	\vspace{2in}
	
	Once you have all written something down, discuss your response in your \textbf{small group}. Write all the different goals on your group's whiteboard.
\end{enumerate}

\WCD

\section{Achieving our goals}

\begin{enumerate}
	\item In the space below, \textbf{individually}, write out a method and/or resource you could use in order to accomplish one of the goals you put up on your group's whiteboard.
	
	\vspace{2in}
	
	Once you have all written something down, discuss your response in your \textbf{small group}. Write all the different goals on your group's whiteboard. (Hint, your syllabus might be helpful!)
\end{enumerate}

\WCD