\section{Check for Understanding: Momentum}
\label{act7.2.3}
\note{For Activity~\ref{act7.2.3} (\about\unit[70]{min})}{
\subsection*{Learning Goals:}
\begin{itemize}
\item Get more practice with both qualitative and analysis of inelastic collisions in both 1-D \& 2-D
\item Get more practice working with vector components of momentum and related quantities
\item Develop a deeper understanding of the independence of motion in perpendicular directions
\item Get more practice applying the impulse = ∆momentum relation
\end{itemize}
}
\note{TAs:}{Be sure to work these out and if you don’t know the answer to these ask at the meeting! }
\begin{overview}

	\textbf{Overview:} In this section, we'll pull everything we've discussed about momentum together to apply our understanding to a few new situations.
	
\end{overview}


\subsection{Collisions in One and Two Dimensions}

\begin{FNTenv}
	\input{U7/fnt7.1.1-7}
\end{FNTenv}

\note{\FNT~\thechapter-\ref{fnt7.2.1-7}}{ask students how they know how to draw each $\vec{p}_{f}$}
\begin{FNTenv}
	\input{U7/fnt7.2.1-7}
\end{FNTenv}

\note{\FNT~\thechapter-\ref{fnt7.2.1-8}}{$1: \Delta T \approx 1.76 \;^\circ C \& \quad 2: \Delta T~\approx0.88 ^\circ C$}
\begin{FNTenv}
	\input{U7/fnt7.2.1-8}
\end{FNTenv}

\begin{enumerate}
	\item In your group, compare your individually created \pcharts{} for \ref{fnt7.1.1-7} and \ref{fnt7.2.1-7}. Note that you do not need to complete the entire chart to find the final velocity. That is, you don't need to find the change in momentum of each asteroid separately. However, finding the individual changes is a good opportunity to hone your skills with momentum conservation.
	
	\textbf{Note:} You may find it useful to choose an $x$-$y$ coordinate system and fill in the chart for \ref{fnt7.2.1-7} with $x$- and $y$-components.
	
	\item On the board, put up complete \pcharts{} (with equations worked through to numerical values) for the 1-D linear collision and the 2-D collision in these two asteroid collision \FNTs.
	
	\item Compare your answers to \ref{fnt7.2.1-8}, come to a consensus, and put your response on the board.
	
	\item \textbf{Extension:} Let's consider the asteroid collision as a ``Many Body Problem:'' Three asteroids collide and stick together. Create a possible \pchart{}.
\end{enumerate}

\WCD

\subsection{Horizontally Thrown and Dropped Balls}
\label{7.2.3c}
\note{For Activity~\ref{7.2.3c} (\about\unit[40]{min})}{
\subsection*{Learning Goals:}
\begin{itemize}
\item Get more practice with both qualitative and analysis of inelastic collisions in both 1-D \& 2-D
\item Get more practice working with vector components of momentum and related quantities
\item Develop a deeper understanding of the independence of motion in perpendicular directions
\item Get more practice applying the impulse  equals change in in momentum relation
\end{itemize}
}
\begin{FNTenv}
	\input{U7/fnt7.2.1-9}
\end{FNTenv}

\begin{FNTenv}
	\input{U7/fnt7.2.1-10}
\end{FNTenv}

\begin{FNTenv}
	\input{U7/fnt7.2.1-11}
\end{FNTenv}

\begin{enumerate}
	\item In your group, compare your individually created \pcharts{} for \ref{fnt7.2.1-9} and \ref{fnt7.2.1-10} and negotiate a consensus for each one.
	
	\item Put your consensus charts on the board. It is simplest to put one header row, with labels $\vec{p}_i$, $\Delta \vec{p}$, and $\vec{p}_f$, and then start a new row in your chart for each time step.
	
	\item Discuss and be prepared to share with the class your response to the prompt, ``Describe in words how the motion changes in the two directions.'' Compare your diagrams from Part~(e) between the two \FNTs. Are the paths you constructed the same? Come to a consensus in your small group on your response to Question~(a) in \ref{fnt7.2.1-11} and be prepared to share it with the whole class.
	
	\item Come to a consensus on Parts~(b) and (c)  in  \ref{fnt7.2.1-11} and be prepared to share them with the whole class.
\end{enumerate}

\WCD