\section{Momentum and Change in Momentum in One Dimension, Part II}

\begin{FNTenv}
	\input{U7/fnt7.1.1-1}
\end{FNTenv}

\begin{FNTenv}
	\input{U7/fnt7.1.1-2}
\end{FNTenv}

\begin{FNTenv}
	\input{U7/fnt7.1.1-3}
\end{FNTenv}

FNTs  7.1.1-1,  7.1.1-2,  and  7.1.1-3
 In Your Small Group
Compare your responses to \FNTs{} 7.1.1-1, 7.1.1-2, and 7.1.1-3 with other members of your small group; come to a consensus on the appropriate \pcharts{} and answers, and put these on the board.

\textit{Added problem:} Draw an appropriately scaled force diagram (for each object) that shows all the forces acting during the interaction (when the impulse occurs); do this for each \FNT.
\WCD

Phenomenon:  Collisions of 2 carts in one dimension, both elastic and inelastic collisions.

Your instructor will assign each group a problem from 1)-3) below and a problem from 4)-5). Use the \pConsModel{} to analyze each of the collisions between two carts in the situations 1- 3 below. We treat the system made up of the two carts as a closed physical system because there is no net external impulse transferred to the system during the collision.

For each collision:
a)	Draw and fill in a \pchart{} to help you describe momentum conservation in this closed physical system.
b)	For each line of the \pchart{}, write an algebraic vector equation, with appropriate subscripts on the symbols, to express what that line tells you about the collision.
c)	Draw a force diagram for each cart that shows the forces during the collision. 
d)   Describe in words what physically happened and then how conservation of momentum applies to each cart and to the system as a whole. Put your,equation and word statement on the board.
e)   Classify each case as elastic or inelastic.

1)	Use two carts of equal mass, physically arranged so the carts will bounce off one another. Start with one cart stationary.
2)	Use two carts of equal mass, physically arranged so the collision ends with the carts locked (stuck together). 
3)	Use two carts of equal mass initially moving toward each other with equal speed and ending with the carts locked.

4)	Place two carts of unequal mass, on the track turned so the collision ends with the carts locked. Start with one cart stationary, and have the other move to collide with it. Make the stationary cart have more mass (repeat, switching carts). 
5)	Place two carts of unequal mass, on the track turned so the collision ends with the carts locked. Start with both carts moving toward each other with the same speed.

Observe what is similar and what is different in your \pcharts{}. What patterns can you observe? Discuss in your group any rules you come up with for the patterns.	
\WCD







 
