\section{Check for Understanding: The Egg Throw}
\label{actegg}
\note{For Activity~\ref{actegg} (\about\unit[30]{min})}{
\subsection*{Learning Goals:}
\begin{itemize}\item Develop an intuitive understanding of how Æt affects net Impulse, J, and net force ?F in collisionss
\end{itemize}

}
\begin{overview}

	\textbf{Overview:} In this section, we'll attempt to explain a new phenomenon (another party trick, if you will) with the models we've accumulated, so far.
	
\end{overview}

\note{Productive ideas students might have:}{
 \begin{itemize}\item The change in velocity is greater when the egg is thrown at the wall (Incorrect - have them re-examine the initial and final states)\item The impulse is greater when the egg is thrown at the wall: The force of the wall is greater, so the impulse must be greater for the wall case.  (Partially  correct, but overall incorrect- Have them think about what else impulse depends on and determine if the impulse is different or the same in both cases.)\item The overall change in momentum is greater when the egg is thrown at the wall: (Incorrect- depending on what they are thinking this could be due to either of the previous alternative conceptions, ask about both.)\item The egg is in contact with the sheet for a longer time than the wall (Correct! Have them explicitly show how this changes the forces acting on both objects, if the changes in momentum are the same.)
 \end{itemize}

}
\textbf{Consider the following two phenomena:}

\begin{enumerate}
	\item Egg thrown at velocity $\vec{v}$ at a wall that stands motionless with respect to the earth.
	
	\item Egg thrown at velocity $\vec{v}$ at a bed sheet that is held by two people standing motionless with respect to the earth.
\end{enumerate}

\noindent For both cases, consider the following interval:

\begin{center}
\begin{tikzpicture}
    % draw horizontal line   
    \draw[->] (0,0) -- (10,0);

    % draw vertical lines
    \foreach \x in {0.5,9.5}
      \draw (\x cm,3pt) -- (\x cm,-3pt);

    % draw nodes
    \draw (0.5,0) node[below=3pt] {the egg flying at top speed} node[above=3pt] {\emph{beginning}};
    \draw (9.5,0) node[below=3pt] {$\vec{v}=0$ in horizontal direction} node[above=3pt] {\emph{end}};
\end{tikzpicture}
\end{center}

\noindent\textbf{Make sure everyone in your group fully understands the ideas behind each question or part below before going on to the next part.}


\begin{enumerate}
	\item In your small groups, predict if the egg will or will not break in either case.
	\item Use your intuition to think about what factors determine whether the egg will break or not. List these factors on your group's board.
	\item Use ideas, models, language, and/or equations from this class to explain why these factors are important. 
\note{whole class discussion:}{Have students share ideas came up when students small groups. What matters? Why? Get students to define the system, identify initial and final states. After some discussion: Do the demo. If students have ideas for other experiments to do to determine what things matter to break the egg, perform them!  Again: Get students to define the system, identify initial and final states.}	
\WCD
\end{enumerate}

\noindent\textbf{Now, go do it!} You will investigate the egg throw cases together as a class.

\begin{itemize}
	\item Come up with a logical argument for why the egg does or does not break in either case.
	\item Write out your argument as you might on a quiz.
	\item Use physics ideas, models, words, and/or equations from class to explain your reasoning.
\end{itemize}


\WCD