\section{More Practice with the \EnergyInteractionModel{}}
\label{act1.1.8}

\begin{overview}

	\textbf{Overview:} We continue our efforts to practice using our models -- particularly the \EnergyInteractionModel{} -- by investigating new phenomena.
	
\end{overview}

\subsection{Cooling Water Below its Freezing Point}

\begin{fnt}
	\input{U1/fnt1.1.4-3}
\end{fnt}

\note{Timing: \unit[\textless3]{min}}{
%Note:  You will have done these FNTs BEFORE coming to class, so you have only a few minutes (\unit[\textless3]{min}) to work on these together in your group.	
}

\noindent On the board, construct the simplest \EnergyDiagram{} that represents a particular model of the process described in this FNT. 

Make sure everyone in your group is ready to explain which elements of your completed diagram represent information that was given, or known, and which elements you had to infer, based on given or known information and the logic of the model? 

\WCD  

\begin{fnt}
	\input{U1/fnt1.1.4-4}
\end{fnt}

\note{Timing: \unit[\textless3]{min}}{
	
}

\noindent Now we'll actually do this experiment:

\begin{enumerate}

	\item On your table, you have an insulated mug and a thermometer. Get some ice from the ice chest on the counter and fill your insulated mug. Measure the temperature inside the ice-filled cup and verify it is at around \unit[0]{\textdegree C}.

	\item Now, add some salt and stir it into the ice with a stirrer (don't use the thermometer; it might break!). Measure the temperature of the salt-ice mixture inside the cup. Add some more salt and repeat the stirring and temperature measurement. How far can you get the temperature to drop?

	\item On the board, list the low temperatures attained by your group.

\end{enumerate}

\noindent Would the following statement be something that would be good to memorize?

\begin{quote}
	{\em ``When bond energy increases, thermal energy must decrease, and vice versa.''}
\end{quote}

\noindent Explain on the board why it would or would not be good to memorize this.

\WCD  

\subsection{Heating Water with Microwaves}

\begin{fnt}
	\input{U1/fnt1.2.1-5}
\end{fnt}

\note{Timing: \unit[\textless3]{min}}{
	
}

\noindent On the board, choose the data from a member of your group, and sketch a graph of cooking power vs.\ amount of water. 

You'll notice that there appears to be some ``missing power.'' That is, the difference in power actually used to heat the water is less than the power used by the unit as stated on a label on the back of the microwave unit.

{[}\textbf{Hint:} Can you feel or hear anything near the back of the microwave unit when it is turned on?{]}

\WCD  
