\section[\motiongraphs{} and Newton's 2nd Law]{Making Sense of Motion through Graphs And Newton's 2nd Law}
\label{act8.2.3}
\note{For Activity~\ref{act8.2.3} (\about\unit[50]{min})
}{
There are additional questions for the students to work on for all these \FNTs.  In some cases, STUDENTS DO NOT PUT UP ANSWERS, but FOCUS ON THE REASONS FOR THE ANSWERS!  
\\[0.25in]
This activity is highly unpopular with some students—but keep emphasizing that they need to know “how to approach and analyze” these questions, not just “get the answer to a multiple choice question.”
\\[0.25in]
Time management:  depending on time constraints or how your \DLM{} is going it might be best to assign different \FNTs{} to the tables.  For example, assign the follow-ups to \FNT~\thechapter-\ref{fnt8.2.1-4} to three tables while the remaining two tables put up \FNT\FNT~\thechapter-\ref{fnt8.2.1-5} follow-up.  Then have a \WC{} discussion.  Then ALL tables put up the \FNT~\thechapter-\ref{fnt8.2.1-6} follow-up.  And after the \WC{} discussion, all groups put up \FNT~\thechapter-\ref{fnt8.2.1-7}.  This way all \FNTs{} are covered; be sure to let the students do the explaining during the \WC{} presentations.
}
\begin{overview}

\textbf{Overview:} We continue our exploration of \motiongraphs{}, especially in the context of Newton's 2nd Law.

\end{overview}

\begin{FNTenv}
	\input{U8/fnt8.2.1-4}
\end{FNTenv}

\noindent Discuss your group's response to the following prompts and then put your responses up on the board.
\begin{enumerate}
	\item Describe in words the motion of the object whose velocity is shown in the graph. Practice walking this graph for the whole class presentation.
	\item Explain exactly how you can determine the acceleration from a graph of velocity vs.\ time.
	\item Construct an acceleration graph from the velocity graph shown in this \FNT{}.
	\item Describe in words how the net force on this object changes from one lettered point to the next.
\end{enumerate}

\WCD

\begin{FNTenv}
	\input{U8/fnt8.2.1-5}
\end{FNTenv}

\noindent Discuss how you can be sure that the values of the acceleration you determined from the velocity graph in regions (a) and (c) are the correct values according to Newton's 2nd law. Show this ``check'' on the board. Note: you do not have to put the graph on the board.\\

\WCD

\newpage

\note{\FNT~\thechapter-\ref{fnt8.2.1-6} part c:}{The big idea here is that the acceleration is related to the change in velocity by definition and to the net force through Newton’s 2nd law.  These have to agree. Often, as in this case, one knows for certain the net force in certain situations, and this can be used to determine the acceleration.
\\[0.25in]
At the points [2] and [3] on the graph the assumption is that these points are during the time the floor is exerting a force on the ball and that the velocity is smoothly varying between these points for simplification.
}

\begin{FNTenv}
	\input{U8/fnt8.2.1-6}
\end{FNTenv}
\note{\FNT~\thechapter-\ref{fnt8.2.1-6} part d:}{
At points [1], [2] and [5] where the velocity is zero, there is a net force acting (unbalanced forces).  Therefore, there must be a non-zero acceleration which is a change in velocity at that instant, regardless of the value of the velocity.  \textbf{Emphasize that unbalanced force diagrams describe a change in motion. } and \text{remind them that a net force is not a real force, but it is the sum of real forces.}
}
\noindent Discuss your group's responses to all parts of this \FNT{} and respond to the following prompts.
\begin{enumerate}
	\item Put your responses to part (a) on the board.
	\item Put only the \textbf{different} \forcediags{} on the board for part (c) and note above each diagram which points -- 1 through 6 -- it applies to. Make sure everyone in your group understands part (d) and is prepared to share with the class.
	\item Make sure everyone in your group understands part (e) and is prepared to share with the class.
\end{enumerate}

\WCD
\begin{FNTenv}
	\input{U8/fnt8.2.1-7}
\end{FNTenv}

\noindent Discuss this \FNT{} in your group and put a \textbf{concise} explanation on the board.\\

\WCD
\begin{FNTenv}
	\input{U8/fnt8.1.1-1}
\end{FNTenv}

\noindent Discuss this \FNT{} in your group, put the three \forcediags{} on the board, and make sure everyone in your group understands these and is prepared to share with the class.\\

\WCD