\section{Newton's Laws and Momentum Conservation}
\label{act8.1.1}
\note{For Activity~\ref{act8.1.1} (\about\unit[65]{min})
}{
\subsection*{Learning Goals:}
\begin{itemize}
\item Develop understanding of the differences between a Newtonian 2nd law approach and a momentum conservation approach and how these relate to energy conservation
\item Get practice figuring out which model/approach can be used to answer particular questions about various phenomena
\item Review Newton’s 1st and 3rd laws
\item Develop understanding of the steps used in the Newtonian 2nd law approach
\end{itemize}
}
\begin{overview}

	\textbf{Overview:} Over the past few weeks, we've dealt a lot with forces, and we know much more about motion in general. We even know that forces cause changes in motion. Sir Isaac Newton, a physicist of the 17th/18th century, formulated three famous laws that powerfully express the relationship between forces and motion. In this next section, we'll discuss these so-called \emph{Newton's Laws}.

\end{overview}

\subsection{Getting started with Newton's Laws}

\begin{FNTenv}
	\input{U8/fnt8.1.0-1}
\end{FNTenv}

\WCD

\newpage

\subsection{Newton's Laws and the \pConsModel{}}

\begin{reading}
\textbf{\textit{Newton's Three Laws of Motion}}

\begin{enumerate}[I.]
	\item Without a net force, there can be no change in the velocity of an object:\footnote{This can be expressed as ``An object in motion remains in motion in a straight line forever unless acted on by an external force;'' and ``An object at rest remains at rest forever unless acted on by an external force.''}
	
	\begin{center}\framebox[1.1\width][c]{If $\sum\vec{F}=0$, then $\Delta\vec{v}=0$.}\end{center}
	
	\item An object will be accelerated if there is a net force acting upon it:
	
	\begin{center}\framebox[1.1\width][c]{$\sum\vec{F}=m\vec{a}$}\end{center}

	\item If object $A$ exerts a force on object $B$, object $B$ \emph{simultaneously} exerts an equal and opposite force on object $A$:\footnote{You may have heard of this as ``For every action, there is an equal and opposite reaction.''}
	
	\begin{center}\framebox[1.1\width][c]{$\vec{F}_\text{A on B} = -\vec{F}_\text{B on A}$}\end{center}
	
\end{enumerate}

\end{reading}

\begin{enumerate}
	\item \label{811,1} Come up with a physical scenario that illustrates each of Newton's three laws. Describe each law in both sentence form and with a concise mathematical expression, specific to your example. Be careful and precise with notation in the algebraic expressions.
\note{\ref{811,1}}{Encourage the students to create and not regurgitate, but be careful with wasting time.  Allot about ten minutes.}	
\filbreak
	\item \label{811,2}
	  % We have to create a parbox here because wrapfigure does not support enumerate environments directly
	  \parbox[t]{\dimexpr\textwidth-\leftmargin}{%
      \vspace{-3mm}
      \begin{wrapfigure}[6]{r}{5cm}
        \centering
        \vspace{-\baselineskip}
			\begin{tikzpicture}[scale=.8, every node/.style={transform shape}]{r}{1}
				\draw[blue] (0,0) ellipse (0.75cm and 0.33cm);
				\draw[blue] (3,1.5) ellipse (0.75cm and 0.33cm);
				\draw[blue,dashed] (1,0) .. controls (2.25,0.25) .. (2.75,1) node[midway, right=4pt, blue] {3rd law};
			\end{tikzpicture}
	  \end{wrapfigure}
      Make a \forcediag{} for each object in each of the following situations. For each situation, circle and connect the forces that are in tandem as third law pairs, as shown.
 
      }
      \note{\ref{811,2}}{We want them to identify Newton’s 3rd law in momentum conservation.  Equal impulses in opposite directions should be in their charts and the impulse equation $\vec{F}_{net}\Delta t = \Delta \vec{p}$ should be on their boards.  Additionally, objects having a constant momentum do not have a net force.  They must understand that force is not needed for constant motion.  Throughout the 7 series many students are not careful distinguishing between the quantity and the change in the quantity.}
           	
	\begin{enumerate}
		\item Refer to the %rocket example of \ref{fnt7.1.1-2}.
		astronaut example from \hyperref[14C.1]{Activity~\ref{14C.1}} on page~\pageref{14C.1}. 
		Recreate a \pchart{} and follow the instructions for the force diagram above. Explain how each of Newton's Laws can be identified in the \pcharts{} and \forcediags{}. Suppose we wanted the rocket to move at a constant speed, is a net force necessary to make this happen?
		
		\item Refer to the boat example of \hyperref[fnt7.1.1-3]{Assignment~\ref{dlm11}-\ref{fnt7.1.1-3}}
		on page \pageref{fnt7.1.1-3}. Recreate a \pchart{} and follow the instructions for the force diagram above. Explain how each of Newton's Laws can be identified in the \pcharts{} and \forcediags{}.
	\end{enumerate}
\end{enumerate}

\WCD

\subsection{Use Newton's Three Laws applied to a system of three objects}

\subsubsection*{\emph{Static} Case: All objects sitting still}

\begin{enumerate}
	\item \label{811A,1}Refer to the picture below of three books sitting on a table that is standing on a floor. Make a separate \forcediag{} for each of the four objects: Books~A, B, and C, and the table. The masses of the books are \unit[0.8]{kg}, \unit[0.2]{kg}, and \unit[0.5]{kg} for Books~A, B, and C, respectively and the mass of the table is \unit[30]{kg}
	\note{For~\ref{811A,1}}{The students may need to be reminded that the $F_{Earth on object}$ is always equal to $mg$ (when the object is near the earth).  Without telling them answers you could help by asking whether the forces in the y-direction are balanced.
\\[0.25in]
The main thing that they should understand is that unbalanced force diagrams describe a change in motion so only in part~\ref{811A,5} will the net force on any object will be non-zero and in part~\ref{811A,5}  all net forces will be non-zero (here you can remind them that it is an object’s mass that determines what force is necessary to yield a given acceleration). 
\\[0.25in]
Only the net force equals mass times acceleration.
\\[0.25in]
Their force diagrams should be properly labeled (always give both objects when naming a force) as $F_{A on B}$ and scaled properly (so the net force should always be proportional to the mass for all objects with the same acceleration).  
\\[0.25in]
The students should write Newton’s 2nd Law expression, $F_{net}= m a$, for each object separately!  Example:  net force on book C = m$_C$a.
}.
	
	\begin{center}
	\begin{tikzpicture}{c}{1}
		% Table
		\draw[double distance = 5pt] (1,0) -- (1,2);
		\draw[double distance = 5pt] (4,0) -- (4,2);
		\draw (0.5,2) rectangle (4.5,2.5) node[midway] {table};
		% Book C
		\draw (1.75,2.5) rectangle (3.5,3.25) node[midway] {C};
		% Book B
		\draw (2,3.25) rectangle (3.25,3.75) node[midway] {B};
		% Book A
		\draw (1.25,3.75) rectangle (3.75,4.5) node[midway] {A};
		% Floor
		\draw (0,0) -- (5,0);
		\foreach \x in {0.5,1,1.5,2,2.5,3,3.5,4,4.5,5}
    			\draw (\x,0) -- (\x-0.25,-0.25);
	\end{tikzpicture}
	\end{center}
	
	\item \label{811A,2}Identify all 3rd law pairs of forces appearing in your \forcediags{} by circling the two forces and connecting as shown in the diagram on the previous page.
	
	\item \label{811A,3}Use Newton's 1st and 3rd laws to numerically determine all of the forces acting on the books and the table. If necessary, redraw your \forcediags{} so they are more to scale.
\end{enumerate}

\subsubsection*{\emph{Dynamic} Cases: Objects moving horizontally and vertically}

\begin{enumerate}
	  \setcounter{enumi}{3}
	\item \label{811A,4}If the books and table together are sliding across the room each at the same constant speed, how would your \forcediags{} change? Show precisely how it would change or explain why it would not.
\note{For \ref{811A,4}}{$F_{B on C }= +5$ N\\		$F_{A on B} = +7$ N\\		$F_{Table on A} = +15$ N\\	      $F_{Floor on table} = +315$ N.}	
	\item \label{811A,5}Now imagine the table is sitting in an elevator that begins to accelerate upward with an acceleration equal to $\unitfrac[2]{m}{s^2}$.
	\begin{enumerate}
		\item Make a new \forcediag{} for each book and determine the forces acting on it.
		\item Create a \pchart{} for at least two of the objects.
		\item Do any of the objects experience a net force? If so, give the magnitude and direction of each.
		\item Is it correct to say a force always equals $m\vec{a}$~?
		\item Is it correct to say that, whenever the net force is zero, the velocity must also be zero?
	\end{enumerate}
\note{For \ref{811A,5}}{
Since there must be a net force pointing up (in +y direction) all forces above must increase; get them to realize this first--have them look at their original force diagrams and ask about net force.  They need to know $F_{E on objects}$ remains same, so tell them.
\\[0.25in]
$F_{B on C }= +6$ N\\		$F_{A on B} = +8.4$ N\\		$F_{Table on A} = +18$ N\\	      $F_{Floor on table} = +378$ N.}	
\end{enumerate}

\WCD

\subsection{Applications of Newton's Laws}

\begin{FNTenv}
	\input{U8/fnt8.1.1-2}
\end{FNTenv}

\vspace{-6pt}
\WCD
\vspace{12pt}

\input{U8/fnts2}