\section{Check for Understanding: Vector Operations}

\begin{overview}

\textbf{Overview:} In this section, we'll apply our newly-gained knowledge about vectors.

\end{overview}

\label{act6.1.3}

\note{For Activity~\ref{act6.1.3} (\about\unit[40]{min})}{
NO Activity Sheet.

In your small group compare your responses to \FNT~\thechapter-\ref{fnt6.1.2-1} through \thechapter-\ref{fnt6.1.2-3} with other members of your small group.  Come to a consensus on an appropriate response to each \FNT{} and be able to make convincing reasons why you know for sure your response is appropriate.  Each person in your group should be prepared to do this for any of the \FNTs.  Nothing on board

Whole Class Sharing
}
\note{Note:}{
Students DO NOT put answers to the \FNTs{} up on the board.   Rather, they are to work these out among themselves at their tables.  Circulate and make sure they are getting them.  \\[0.25in]Then conduct a whole class discussion, going through each one as briefly as possible and calling on students to give their reasons for their answer.  Stress that they should know for sure what the appropriate response should be.\\[0.25in]Make sure students understand for \FNT~\ref{fnt6.2.1-1} that the magnitude of a vector is always a positive number.
}

\begin{FNTenv}
	\input{U6/fnt6.1.2-1}
\end{FNTenv}

\vspace{-10pt}
\WCD
\vspace{3pt}

\begin{FNTenv}
	\input{U6/fnt6.1.2-2}
\end{FNTenv}

\vspace{-10pt}
\WCD

\begin{FNTenv}
	\input{U6/fnt6.1.2-3}
\end{FNTenv}

\vspace{-10pt}
\WCD
\vspace{3pt}

\begin{FNTenv}
	\input{U6/fnt6.1.2-4}
\end{FNTenv}

\vspace{-10pt}
\WCD