\section[Check for understanding: More Vectors]{Check for understanding: Force, Velocity, and Momentum Vectors}
\label{act6.1.3b}
\note{For Activity~\ref{act6.1.3b} (\about\unit[40]{min})}{
In  small groups, Compare  responses to \FNT~\thechapter-\ref{fnt6.1.2-4} through \thechapter-\ref{fnt6.1.2-7} and \FNT~\thechapter-\ref{fnt6.2.1-1} with other members of your small group.  Come to a consensus on an appropriate response to each \FNT{} and be able to make convincing reasons why you know for sure your response is appropriate.  Each person in your group should be prepared to do this for any of the \FNTs.  Nothing on boardWhole Class Sharing
}

\begin{overview}

\textbf{Overview:} In this section, we'll practice what we've learned about force and velocity vectors, so far.

\end{overview}

\note{for \FNT~\thechapter-\ref{fnt6.1.2-4} }{
$\vec{F}_{1} = (-4, 2)$; $\vec{F}_{2} = (8, 9)$;  $\Sigma \vec{F} = (-8, 0)$
\\[0.25in]Answer should be found graphically:Solution: $\vec{F}_{3} $ = (-12, -11)
}
\begin{FNTenv}
	\input{U6/fnt6.1.2-4}
\end{FNTenv}


\note{for \FNT~\thechapter-\ref{fnt6.1.2-5} }{
$\vec{F}_{1} = (-4, 4)$; $\vec{F}_{2} = (-14, 0)$
\\[0.25in]Answer should be found graphically:Solution: $\vec{F}_{3} $ = (0, -4); $\vec{F}_{4} $ = (18, 0); 
}\begin{FNTenv}
	\input{U6/fnt6.1.2-5}
\end{FNTenv}

\WCD
\vspace{12pt}

\note{for \FNT~\thechapter-\ref{fnt6.1.2-6} }{
$\vec{F}_{1} = (4.33, 2.5)$; $\vec{F}_{2} = (0, 15)$;  
\\[0.25in]Answer should be found using trigonometry:Solutions: \\
a) $\Sigma \vec{F} $ = (4.33, 17.5)\\
b) $\Sigma \vec{F} $ = 18.0 \@ 76.1$^{\circ}$
}
\begin{FNTenv}
	\input{U6/fnt6.1.2-6}
\end{FNTenv}

\WCD
\vspace{12pt}
\newpage

\note{for \FNT~\thechapter-\ref{fnt6.1.2-7} }{
a) Solution:  velocity vectors should be same magnitude pointing in the direction the cart is moving (so 2 equal and opposite velocity vectors)b) Solution: Because cart 1 is half the mass of cart 2, the momentum vector for cart 1 should be half the magnitude of cart 2Õs momentum vector. They should point in the direction the carts are moving respectively. Check to see that the student has drawn a picture and defined which way the carts are moving.c) Check to see that students added the vectors tip to tail and that $p_{total}$ is not equal to 0.   
}
\begin{FNTenv}
	\input{U6/fnt6.1.2-7}
\end{FNTenv}

\WCD
\vspace{12pt}

\note{for \FNT~\thechapter-\ref{fnt6.2.1-1} }{
Go over student questions. Students were to rework parts of \hyperref[act6.2.1]{Activity~\ref{act6.2.1}} on page \pageref{act6.2.1} (spring scale activity) they found confusing.  
}
\begin{FNTenv}
	\input{U6/fnt6.2.1-1}
\end{FNTenv}

\WCD