\section[More Modeling of Mechanical Energy Systems]{Practicing Graphical and Quantitative Modeling of Mechanical Energy Systems}
%\section{Follow-up of Module 2.2-2.3 FNTs}
\label{act2.3.2}

\begin{overview}

\textbf{Overview:} Before we introduce a new class of physical phenomena, \textbf{\emph{forces}}, we want to make sure you get a bit more practice modeling phenomena using the tools we have accumulated until now, especially the method of graphing energy amounts introduced in the last activities and the carefully crafted model-based, scientific arguments we've been practicing for a while.
	
\end{overview}

\subsection*{We've done a practice activity like this before:}

At home, please work through all the FNTs listed in this activity. In class, each group will work on a portion of these FNTs to come to a consensus before we discuss the scenarios with the whole class.\\

\begin{fnt}
	\input{U2/fnt2.2.3-1}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.2.1-7}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.2.1-8}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.3.1-1}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.3.1-2}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.3.1-3}
\end{fnt}

\begin{center}\noindent\textbf{Each group is responsible for putting one of the following on the board.\\ Write so that all other groups can easily follow your presentation!}\end{center}

\noindent\framebox[1.1\width][c]{\textbf{Group 1}}\\

\noindent\ref{fnt2.3.1-1}\\

\noindent For each of Parts~\eqref{fnt2.3.1-1a} and \eqref{fnt2.3.1-1b} of this FNT, make a simple sketch (not a graph) showing the origin 
(where $y = 0$), the ball's initial position, positions $y_\text{max}$ and $y_\text{min}$, and the floor. Then, for each of your two sketches, show how to find the maximum and minimum values of gravitational potential energy, and the total energy.\\

\noindent Be ready to explain how changing the location of where $y = 0$ will affect $PE_\text{gravity}$.\\

\noindent\framebox[1.1\width][c]{\textbf{Group 2}}\\

\noindent\ref{fnt2.3.1-2}

\begin{enumerate}[(a)]
	\item Draw $PE_\text{spring-mass}$ and $E_\text{total}$ (but not $KE$) on a graph of Energy vs.\ ``Distance ($x$) from equilibrium'' for the case of the mass displaced \unit[5]{cm} from equilibrium and released. Clearly label the maximum and minimum values of $PE_\text{spring-mass}$.
	
	\item Demonstrate how to use point by point plotting to graph the $KE$ by doing the following: For at least two different values of $x$, use energy conservation in the form: ``$KE = E_\text{total} - PE$'' to plot a point representing the $KE$. Label the graph clearly showing $PE$, $E_\text{total}$, and $KE$ at each point. In the Whole Class Discussion you can show how to then fill in the $KE$ by sketching a dashed line connecting the points with a smooth curve.
	
	\item On the same graph, quickly draw $PE_\text{spring-mass}$ and $E_\text{total}$ (but not $KE$) for the case of the mass displaced \unit[2.5]{cm} from equilibrium.
\end{enumerate}

\noindent\framebox[1.1\width][c]{\textbf{Group 3}}\\

\noindent\hyperref[fnt2.2.1-7a]{\ref*{fnt2.2.1-7} Part~\ref*{fnt2.2.1-7a}}\\

\noindent Construct a complete \EnergyDiagram{} with accompanying equations as directed in Part~\eqref{fnt2.2.1-7a} of this FNT, and be ready to explain if you have enough information to determine the speed of the mass.\\

\noindent\hyperref[fnt2.2.1-7b]{\ref*{fnt2.2.1-7} Part~\ref*{fnt2.2.1-7b}}\\

\noindent Construct a complete \EnergyDiagram{} with accompanying equations as directed in Part~\eqref{fnt2.2.1-7b} of this FNT, and be ready to explain if you have enough information to determine the increase in thermal energy.\\
 
\noindent\framebox[1.1\width][c]{\textbf{Group 4}}\\

\noindent\hyperref[fnt2.2.1-8a]{\ref*{fnt2.2.1-8} Part~\ref*{fnt2.2.1-8a}}\\

\noindent Construct a complete \EnergyDiagram{} with accompanying equations as directed in Part~\ref*{fnt2.2.1-8a} of this FNT, and be ready to explain if you have enough information to determine the speed of the skier on the middle part of the hill.\\

\noindent\framebox[1.1\width][c]{\textbf{Group 5}}\\

\noindent\hyperref[fnt2.2.1-8b]{\ref*{fnt2.2.1-8} Part~\ref*{fnt2.2.1-8b}}\\

\noindent Construct a complete \EnergyDiagram{} with accompanying equations as directed in Part~\eqref{fnt2.2.1-8b} of this FNT, and be ready to explain if you have enough information to determine the speed of the skier at the bottom of the hill.\\

\noindent Could you have used different initial values of energy system indicators to answer the same question? Briefly show/explain on the board.\\

\noindent\framebox[1.1\width][c]{\textbf{Group 6}}\\

\noindent\ref{fnt2.3.1-3}\\

\noindent Put your response for this FNT on the board. Be sure to show how you determined the total energy of the physical system.\\

\noindent Is this the only correct value of total energy for the system? Briefly show/explain.\\

\noindent\framebox[1.1\width][c]{\textbf{All Groups}}\\

\noindent\ref{fnt2.2.3-1}\\

\noindent Put your response for this FNT on the board.\\

\WCD