\section{Quantitative Modeling of Mechanical Energies}
\label{act2.2.1}
\note{Think and Discuss }{
Do one question at a time as a \WC{}.  Give them 1-2 minutes to discuss in their \SG{}, then spend two minutes discussing as a \WC{} and repeat with each subsequent question. 
}
\note{Help with Algebraic Signs}{
Your main job here is to force the students to go through the complete modeling system without taking short cuts!!!!!!  Only after getting general energy conservation equations following from their diagrams are they ready to put in the algebraic expressions and solve numerically.  [Which they will do as \FNTs]. 
\begin{enumerate}
\item Make sure they are as specific as possible with initial and final conditions for the two energy systems.  
\item This question is intended to encourage them to connect the abstract model with the phenomenon.
\item Make sure they are explicit about checking the signs of the terms with the increases and decreases of energy. 
\item $(y_f - y_i) = \frac{(v_i^2 –v_f^2)}{2g}$.  $(y_{max} - y_i) = \frac{v_i^2 }{2g}$. 
\item They would need values for g and $y_i$. 
\end{enumerate}

}
\begin{overview}

	\textbf{Overview:} There are interesting features of some of the Mechanical Energy systems that only become apparent in the algebraic expression for the change in energy. These features can help us tremendously in making sense of physical phenomena. To remind you, the energy systems we are currently working with are $KE_\text{translational}$, $KE_\text{rotational}$, $PE_\text{gravity}$, $PE_\text{spring-mass}$, and $PE_\text{spring}$. In this activity, we will explore some quantitative features of these energy systems.
	
\end{overview}


\subsection{Relationships between Energy Systems and Indicators}

 In your small group, take a few minutes to think about and discuss {\em each} of the questions below. Each question will be followed immediately by a short \WCD

\begin{enumerate}
	\item What are the indicators of change in each of the Mechanical Energy systems?
	\note{}{$PE_{gravity}$: Height (y). Ask them, “Height from what?”  They must choose a reference point.  KE: speed (v).  PEspring and PEmass-spring : distance from equilibrium position (y or x). }
	\item \begin{enumerate}
		\item Which of these energies depend on the square of the indicator and which depend on the first power of the indicator?
		\item Which of these energies depend on which direction something moves?
		\item What is the connection between the two previous questions?
	\end{enumerate}
		\note{}{The point here is to see that a squared term removes directional dependence (as would an absolute value or any even power), but a term that is an odd power (such as linear) does have direction.  $PE_{gravity}$ and $KE$ both depend on the mass, but only $PE_{gravity}$ depends on the weight (which is itself directly proportional to mass, with ``g'' as the constant of proportionality).  The spring potentials don’t depend on mass.  This may seem bizarre to students for the case of the mass-spring, but usually someone will insist that since it is not in the equation it can’t depend on the mass.  It might be a good idea to have gone through the derivation of that equation for the mass spring before the \DLM{} (even if you have done it before) just so you are convinced that all that matters is the distance from equilibrium and the spring constant.  All that changes when we include the mass is the location of the equilibrium position.
}
	\item Which of these energy systems depend on the mass of the object and which depend on the weight? Why does this matter?
\end{enumerate}

\noindent
The fact that some indicators are linear and some are quadratic has additional consequences as the next two questions illustrate:

\begin{enumerate}\setcounter{enumi}{3}	
	\item Consider a heavy ball. Would it take the same amount of work to vertically lift it from \unit[25]{cm} to \unit[30]{cm} as it does to lift it from \unit[30]{cm} to \unit[35]{cm}? If not, which situation requires more work? Why?
	\item Does it take the same amount of work to speed your car up from \unitfrac[25]{m}{s} to \unitfrac[30]{m}{s} as it does to speed it up from \unitfrac[30]{m}{s} to \unitfrac[35]{m}{s}? If not, situation requires more work? Why?
\end{enumerate}
	\note{}{This is here to prevent students from mistakenly trying to use (vf-vi)2 instead of vf2-vi2 when determining changes in kinetic energy.  Plugging in numbers will convince skeptics that these are not the same expressions.  
}	
\subsection{Keeping Track of Directionality}
\label{act2.2.1b}

We are about to begin using the \EnergyInteractionModel{} to predict quantitative properties of various phenomena. A potential pitfall of quantitative modeling is that we sometimes tend to lose track of why we are doing something once we start calculating numbers. It is especially easy to lose track of \emph{directionality}, which is mathematically expressed in \emph{algebraic signs}. However, our \EnergyDiagrams{} tell us the signs of the various terms in the conservation of energy equation most of the time. Therefore, don't forget to use the \EnergyDiagrams{} to check the signs as you begin to model scenarios quantitatively!

\noindent\textbf{The Phenomenon:} Christine throws a ball straight up, letting go of the ball at a height of $y_i$ above the ground. When she lets go, the ball has an initial speed $v_i$. The ball travels straight up to its maximum height ($y_{max}$) and falls back down. Assume the frictional effects from air resistance are insignificant.

\subsubsection*{Constructing a particular model to find the maximum height:}

\begin{enumerate}
	\item Construct a particular model of this phenomenon that can be used to determine the maximum height of the ball. ($y_f = y_{max}$) Put a sketch of the path of the ball and a complete \EnergyDiagram{} (with accompanying energy conservation equation) on the board [leave half the board free for the following questions]. What do you know about the ball's speed at its maximum height when it's thrown straight up?
	
	\item Indicate the initial and final positions of the ball on your sketch that correspond to the initial and final conditions in your \EnergyDiagram{}.
	
	\item On the board, rewrite the energy conservation equation by replacing the two terms with algebraic expressions for the changes in energy of the energy systems. Does the resulting algebraic sign of each term in your energy conservation equation agree with the increases and decreases in energy systems in your diagrams?
	
	\item Solve the equation for ($y_f - y_i$). Does the sign of ($y_f - y_i$) make sense for this particular physical situation?
	\label{act2.2.1b4}
	
	\item If you knew the numerical value of $v_i$, could you calculate the maximum height?
\end{enumerate}

\WCD