\section[More Modeling with Mechanical Energy]{More Modeling of Scenarios involving Mechanical Energy Systems}
\label{act2.2.2}

\begin{overview}
	
	\textbf{Overview:} In this activity, we will explore additional scenarios that are related to phenomena we've already discussed. Here, we add some variations to the scenarios and answer some different questions we haven't asked yet.
	
\end{overview}

\noindent\textbf{Note:} Remember Christine throwing a ball in the air in \hyperref[act2.2.1b]{Activity~\ref*{act2.2.1b}}?

\begin{fnt}
	\input{U2/fnt2.2.1-1}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.2.1-2}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.2.1-3}
\end{fnt}

\begin{fnt}
	\input{U2/fnt2.2.1-4}
\end{fnt}

\noindent After throwing her ball in the air a few times, Christine is tired of playing with the ball and instead moves on to water balloons (much more fun, right?). She stands on top of the Science Building, ready to launch her water balloon.

\begin{fnt}
	\input{U2/fnt2.2.1-5}
\end{fnt}

\noindent Eventually, Christine grows tired of throwing and dropping things. She goes back into the Science Building to play with a mass that's hanging on a spring in one of the laboratory rooms.

\begin{fnt}
	\input{U2/fnt2.2.1-6}
\end{fnt}


\begin{center}\noindent\textbf{Each group is responsible for putting one of the following on the board.\\ Write so that all other groups can easily follow your presentation!}\end{center}


\noindent\framebox[1.1\width][c]{\textbf{Group 1}}\\

\noindent\ref{fnt2.2.1-1} \& \ref{fnt2.2.1-4} (\unit[\textless 5]{min}) 
 
 \begin{itemize}
 	\item[\textbf{Read:}] You should already have used the principle of energy conservation to develop an equation for the change in height of a ball thrown straight up in the air (from \hyperref[act2.2.1b]{Activity~\ref{act2.2.1b}}).
	
	\item[\textbf{Do:}] Write a sentence or two explaining what fundamental feature of the \EnergyInteractionModel{} ``accounts for'' why changing the location of $y = 0$ does not change your calculation of the ball's maximum height above the floor. [\textbf{Hint:} think about the general form of the algebraic expression of energy conservation.]
\end{itemize}

\noindent
\ref{fnt2.2.1-2} (\unit[\textless 5]{min})

\begin{itemize}
	\item[\textbf{Read:}] When you model the process described in \ref{fnt2.2.1-2} in two different ways, i.e., using an interval corresponding to the overall process in versus splitting the overall process into two contiguous pieces with separate intervals corresponding to each part, you should get the same result for the speed of the ball at \unit[4]{m} above the floor.
	
	Check with your instructor for the correct numerical answer.
	
	\item[\textbf{Do:}] In terms of the \EnergyInteractionModel{}, why is it not necessary to divide the overall process into two pieces in order to find the speed of the ball at \unit[4]{m} above the floor falling down? 		 
\end{itemize}


\noindent\framebox[1.1\width][c]{\textbf{Group 2}}\\

\noindent\ref{fnt2.2.1-3} (\unit[\textless 10]{min})\\

\noindent Construct one or two \EnergyDiagrams{} that you can use to explain how you know that an object thrown vertically upward will have the same speed as it comes down through any point that it had going up through that same point.\\


\noindent\framebox[1.1\width][c]{\textbf{Group 3}}\\

\noindent\ref{fnt2.2.1-5} (\unit[\textless 10]{min})\\

\noindent Construct a complete \EnergyDiagram{} for the process described in \hyperref[fnt2.2.1-5a]{Part~(\ref*{fnt2.2.1-5a})} of this FNT.\\


\noindent\framebox[1.1\width][c]{\textbf{Group 4}}\\

\noindent\hyperref[fnt2.2.1-6a]{\ref*{fnt2.2.1-6}, Part~(\ref*{fnt2.2.1-6a})} 	(\unit[\textless 10]{min})\\

\noindent Construct a complete \EnergyDiagram{} for the process described in \hyperref[fnt2.2.1-6a]{Part~(\ref*{fnt2.2.1-6a})} of this FNT.\\


\noindent\framebox[1.1\width][c]{\textbf{Group 5}}\\

\noindent\hyperref[fnt2.2.1-6b1]{\ref*{fnt2.2.1-6}, Parts~(b)-(i) \& (b)-(ii)} (\unit[\textless 10]{min})\\

\noindent Construct a complete \EnergyDiagram{} for the process described in \hyperref[fnt2.2.1-6b1]{Parts~(b)-(i)} and \hyperref[fnt2.2.1-6b2]{(b)-(ii)} of this FNT.\\


\noindent\framebox[1.1\width][c]{\textbf{Group 6}}\\

\noindent\hyperref[fnt2.2.1-6b3]{\ref*{fnt2.2.1-6}, Part~(b)-(iii)} (\unit[\textless 10]{min})\\

\noindent Construct a complete \EnergyDiagram{} for the process described in \hyperref[fnt2.2.1-6b3]{Part~(b)-(iii)} of this FNT.\\

\WCD