\label{Unit0}

%\setcounter{chapter}{-1}
%\chapter[\chaptername\thechapter]{\chapterlongname \thechapter}
%	No class meeting.
	
%\chapter[\chaptername\thechapter]{\chapterlongname \thechapter}
\chapter[Introduction]{Introduction}
	\section{Introduction to the Course Format}
		This class is run in a way that is likely different from what you are used to. {\em Active} participation is {\em essential} for your success in the course.
		
		To help you become a productive and successful member of our class community, we will start off with an introductory activity that will allow you to familiarize yourself with the course format. Since our philosophy about how you learn best in this course most likely differs from other instructors', we will do everything we can to help you get into the habit of participating actively and asking questions as soon as you have them.

	\section{Pretest}
		Our physics department is very interested in finding out about the effectiveness of our courses. Therefore, in many courses, students are asked to complete a pre-test at the beginning of the semester (and a post-test at the end) that aims to measure how well a particular course helps students understand certain physics topics.
		
		In the first discussion lab meeting, you will be taking a pretest to show what you know coming into the class. There is absolutely no need to study for this ahead of time. This test is \textbf{\emph{not}} graded (however, we see taking the test as part of your active participation in this course). We may use the overall results to help us decide what to focus on teaching during the semester.